### 2017-12-13 article/article.tex
latex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Machine Learning @ PUC-Rio 2017.2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ian Albuquerque Raymundo da Silva - 1310451
% Clara de Mattos Szwarcman - 1310351
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.4 (15/5/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside,twocolumn]{article}

\usepackage{blindtext} % Package to generate dummy text throughout this template 
\usepackage[utf8]{inputenc}

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Supervised Learning with Fashion MNIST $\bullet$ December 2017 $\bullet$ Machine Learning @ PUC-Rio} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

\usepackage{hyperref} % For hyperlinks in the PDF

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{Supervised Learning with Fashion MNIST} % Article title
\author{%
\textsc{Clara de Mattos Szwarcman}\thanks{Clara's student ID: 1310351} \\[1ex] % Your name
\normalsize Pontifícia Universidade Católica do Rio de Janeiro \\ % Your institution
\normalsize \href{mailto:clara_szw@hotmail.com}{clara\_szw@hotmail.com} % Your email address
\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
\textsc{Ian Albuquerque Raymundo da Silva}\thanks{Ian's student ID: 1310451} \\[1ex] % Second author's name
\normalsize Pontifícia Universidade Católica do Rio de Janeiro \\ % Second author's institution
\normalsize \href{mailto:ian.albuquerque.silva@gmail.com}{ian.albuquerque.silva@gmail.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent \blindtext % Dummy abstract text - replace \blindtext with your abstract text
\end{abstract}
}

%----------------------------------------------------------------------------------------

\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Introduction}

\lettrine[nindent=0em,lines=3]{T} he MNIST dataset is considered the "hello world" of Machine Learning.
Current results achieve over 99.7\% accuracy using different techniques
\cite{LWan:2013dg} \cite{DCirean:2012dg} \cite{ISato:2015dg} \cite{JRChang:2015dg} \cite{CYLee:2015dg}.
Also, many good techniques do not work well on this dataset because of its simplicity \cite{CFran:2017dg}.
Because of this, many consider this an improper

%------------------------------------------------

\section{Methods}

Maecenas sed ultricies felis. Sed imperdiet dictum arcu a egestas. 
\begin{itemize}
\item Donec dolor arcu, rutrum id molestie in, viverra sed diam
\item Curabitur feugiat
\item turpis sed auctor facilisis
\item arcu eros accumsan lorem, at posuere mi diam sit amet tortor
\item Fusce fermentum, mi sit amet euismod rutrum
\item sem lorem molestie diam, iaculis aliquet sapien tortor non nisi
\item Pellentesque bibendum pretium aliquet
\end{itemize}
\blindtext % Dummy text

Text requiring further explanation\footnote{Example footnote}.

%------------------------------------------------

\section{Results}

\begin{table}
\caption{Example table}
\centering
\begin{tabular}{llr}
\toprule
\multicolumn{2}{c}{Name} \\
\cmidrule(r){1-2}
First name & Last Name & Grade \\
\midrule
John & Doe & $7.5$ \\
Richard & Miles & $2$ \\
\bottomrule
\end{tabular}
\end{table}

\blindtext % Dummy text

\begin{equation}
\label{eq:emc}
e = mc^2
\end{equation}

\blindtext % Dummy text

%------------------------------------------------

\section{Discussion}

\subsection{Subsection One}

A statement requiring citation \cite{Figueredo:2009dg}.
\blindtext % Dummy text

\subsection{Subsection Two}

\blindtext % Dummy text

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem{LWan:2013dg}
L. Wan, M. Zeiler, S. Zhang, Y. LeCun, and R. Fergus, “Regularization of neural networks using dropconnect,” Icml, no. 1, pp. 109–111, 2013.

\bibitem{DCirean:2012dg}
D. Cirean, U. Meier, and J. Schmidhuber, “Multi-column Deep Neural Networks for Image Classification,” International Conference of Pattern Recognition, no. February, pp. 3642–3649, 2012.

\bibitem{ISato:2015dg}
I. Sato, H. Nishimura, and K. Yokoi, “APAC: Augmented PAttern Classification with Neural Networks,” Arxiv, 2015.

\bibitem{JRChang:2015dg}
J.-R. Chang and Y.-S. Chen, “Batch-normalized Maxout Network in Network,” Arxiv, 2015.

\bibitem{CYLee:2015dg}
C.-Y. Lee, P. W. Gallagher, and Z. Tu, “Generalizing Pooling Functions in Convolutional Neural Networks: Mixed, Gated, and Tree,” in Proceedings of the 19th International Conference on Artificial Intelligence and Statistics, 2015, pp. 464–472.

\bibitem{CFran:2017dg}
Chollet, François. "Many good ideas will not work well on MNIST (e.g. batch norm). Inversely many bad ideas may work on MNIST and no transfer to real CV." 13 April 2017, 11:51 a.m. Tweet.

\end{thebibliography}

%----------------------------------------------------------------------------------------

\end{document}

### 2017-12-13 algorithms/cv_svm.py

@@ -1,0 +1,193 @@
+# 80.36999999%
+
+from sklearn.svm import SVC
+import numpy as np
+import matplotlib.pyplot as plt
+import utils.viewer
+from scipy.ndimage import rotate
+from scipy.ndimage import center_of_mass
+from scipy.ndimage import shift, binary_fill_holes
+from skimage.transform import rescale
+# import cv2
+from skimage.feature import corner_harris, peak_local_max
+from skimage import filters
+from skimage import exposure
+from skimage.segmentation import active_contour
+from skimage.segmentation import mark_boundaries, find_boundaries
+from skimage.feature import canny
+from skimage.morphology import watershed
+from skimage.morphology import square, dilation, closing
+
+NUM_FEATURES = 10
+BLOCK_SIZE = 2
+K_SIZE = 5
+K_HYPER = 0.02
+
+def normalize(a):
+    return (a - np.mean(a)) / max(0.001, np.std(a))
+
+def train(x_data,y_data,classes):
+    global NUM_FEATURES
+    global BLOCK_SIZE
+    global K_SIZE
+    global K_HYPER
+
+    x_data = x_data / 255.0
+    y_data = y_data
+
+    print(x_data.shape)
+
+    new_x_data = []
+    new_y_data = []
+
+    for x,y in zip(x_data, y_data):
+        img = x.reshape((28,28))
+
+        img = canny(img)
+        img = closing(img, square(3))
+        img = filters.gaussian(img)
+        # img = binary_fill_holes(img)
+        # img = exposure.equalize_hist(img)
+        # img = filters.sobel(img)
+        # img = img ** 2
+        # img[img > np.max(img)*0.1] = 1.0
+        # img[img <= np.max(img)*0.1] = 0.0
+
+        # s = np.linspace(0, 2*np.pi, 400)
+        # x = 14 + 7*np.cos(s)
+        # y = 14 + 7*np.sin(s)
+        # init = np.array([x, y]).T
+
+        # snake = active_contour(filters.gaussian(img, 2),
+        #                     init, alpha=0.015, beta=1, gamma=0.001)
+
+        # print(snake)
+        # utils.viewer.view_img(img.flatten())
+
+        # sn = np.zeros((28,28))
+        # for pt in snake:
+        #     sn[int(pt[0]), int(pt[1])] = 1
+        # utils.viewer.view_img(sn.flatten())
+
+        #-----V
[…]

### 2017-12-13 algorithms/knn_euclidian.py

@@ -40,7 +40,7 @@ def from_data_to_haar(data):
     new_data = np.zeros((32, 32))
     new_data[:28, :28] = data.reshape((28, 28))
 
-    for k in xrange(5):
+    for k in range(5):
         k = 5 - k
         new_data[:2**k, :2**k] = np.apply_along_axis(haar_transform, 0, new_data[:2**k, :2**k])
         new_data[:2**k, :2**k] = np.apply_along_axis(haar_transform, 1, new_data[:2**k, :2**k])

### 2017-12-13 algorithms/svm.py

@@ -56,7 +56,7 @@ from skimage.transform import rescale
 # 100 | 43.69 | 64.21
 # 1000 | 59.10 | 78.56
 # 5000 | ? | 83.91%
-# 60k | 87.23 |
+# 60k | 87.23 | 89.53%
 
 # -------------------------------
 
@@ -108,7 +108,7 @@ def train(x_data,y_data,classes):
 
     print(x_data.shape)
 
-    svc = SVC(C=10, kernel='poly', verbose=True)
+    svc = SVC(C=10**6, kernel='rbf', gamma=4*(10**(-7)), verbose=True)
 
     svc.fit(x_data,y_data)
 

### 2017-12-13 tensorFlowPy3.py

@@ -20,6 +20,7 @@ from __future__ import print_function
 import numpy as np
 import tensorflow as tf
 import utils.reader
+from scipy.ndimage import rotate
 
 tf.logging.set_verbosity(tf.logging.INFO)
 
@@ -146,9 +147,19 @@ def main(unused_argv):
   eval_data = eval_data.astype(np.float32)
   eval_data = np.multiply(eval_data, 1.0 / 255.0)
 
+  new_train_data = []
+  new_train_labels = []
+  for x, y in zip(train_data, train_labels):
+      img = x.reshape((28,28))
+      for da in range(-5, 5):
+          rot = rotate(img, da, reshape=False)
+          new_train_data.append(rot.flatten())
+          new_train_labels.append(y)
+  train_data = np.array(new_train_data)
+  train_labels = np.array(new_train_labels)
+  
   train_labels = np.asarray(train_labels, dtype=np.int32)
   eval_labels = np.asarray(eval_labels, dtype=np.int32)
-
 
   # Create the Estimator
   mnist_classifier = tf.estimator.Estimator(

### 2017-12-13 vgg.py

@@ -186,7 +186,7 @@ def main(unused_argv):
       shuffle=True)
   mnist_classifier.train(
       input_fn=train_input_fn,
-      steps=140000,
+      steps=300000,
       hooks=[logging_hook])
 
   # Evaluate the model and print results

### 2017-12-13 article/article.tex
article update

@@
 Also, many good techniques do not work well on this dataset because of its simplicity \cite{CFran:2017dg}.
-Because of this, many consider this an improper
+With that in mind, the Fashion MNIST dataset \cite{FashionMNIST} was created. It has same size and format
+of the MNIST dataset (70.000 grayscale images of size 28x28 labeled into 10 different classes) meaning that
+it should be as simple to use, but its images consist of fashion items which are supposedly harder to
+classify.
+
+The goal of this work is to explore different techniques of supervised learning for classifying the images
+in the Fashion MNIST dataset. We want to measure the accuracy of our tests and compare them with different
+results on the same dataset, while also trying to obtain some intuition behind the data.
+
+%----------------------------------------------------------------------------------------
+
+\section{Preparation}
+
+The Fashion MNIST is already subdivided into two sets. A set of 60.000 images (the training set)
+and a set of 10.000 images (the test set). The idea is to learn with the training set and then
+evaluate the performance of our trained model with the test set.
+
+We will be using the standard accuracy as a metric for our tests:
+\begin{equation}
+\label{eq:acc}
+accuracy = \frac{\#(correct\_classifications)}{\#(test\_set\_size)}
+\end{equation}
+
+The dataset is already provided as a list of (28*28)+1 sized vectors corresponding
+to each of the 28*28 pixels of the image plus 1 entry for the classification.
+Since each pixel value was an integer from 0 to 255, we have opted to divide
+each value by 255 to achieve features that goes from 0 to 1.
+
+%----------------------------------------------------------------------------------------
+
+\section{Known Results}
+
+The Fashion MNIST repository contains some benchmarks using the python library
+scikit-learn \cite{scikitlearn} \cite{scikitlearnbenchmark}. They are not meant
+to be efficient or good, but they work as a baseline for our project.
+The best result (corresponding to the best selection of parameters tested)
+of each algorithm are displayed in table \ref{table:scikit-benchmark}.
+
+\begin{table}
+\centering
+\begin{tabular}{llr}
+\toprule
+Algorithm Name & Best Accuracy (\%) \\
+\midrule
+SVC & $89.7$ \\
+Gradient Boosting & $88.8$ \\
+Random Forest & $87.9$ \\
+MLP & $87.7$ \\
+K-Neighbors & $86.0$ \\
+Logistic Regression & $84.0$ \\
+SGD & $82.9$ \\
+Decision Tree & $80.1$ \\
+\bottomrule
+\end{tabular}
+\caption{Fashion MNIST Scikit-Learn Benchmark \cite{scikitlearnbenchmark} }
+\label{table:scikit-benchmark}
+\end{table}
+
+The current state of art for the Fashion MNIST dataset is a recent one, with 96.3\% accuracy using Wide
+Residual Networks using random erasing data augmentation \cite{randomerasingdataaugmentationpaper}.
+We will consider this as the ceiling accuracy for our project.
 
@@
 
+\bibitem{FashionMNIST}
+Fashion-MNIST: a Novel Image Dataset for Benchmarking Machine Learning Algorithms. Han Xiao, Kashif Rasul, Roland Vollgraf
+
+\bibitem{scikitlearn}
+API design for machine learning software: experiences from the scikit-learn project, Buitinck et al., 2013
+
+\bibitem{scikitlearnbenchmark}
+Zalando Research. Fashion MNIST Scikit-Learn benchmark. http://fashion-mnist.s3-website.eu-central-1.amazonaws.com/
+
+\bibitem{randomerasingdataaugmentationpaper}
+Zhong Z., Zheng L., Kang G., Li S., Yang Y. . Random Erasing Data Augmentation. ArXiv e-prints 1708.04896 2017
+
 \end{thebibliography}

### 2017-12-13 vgg.py

@@ -186,7 +186,7 @@ def main(unused_argv):
       shuffle=True)
   mnist_classifier.train(
       input_fn=train_input_fn,
-      steps=300000,
+      steps=100000,
       hooks=[logging_hook])
 
   # Evaluate the model and print results

### 2017-12-13 article/article.tex
article.tex

@@
 \usepackage[utf8]{inputenc}
+\usepackage{graphicx}
 
@@
 
+\section{Approaches}
+
+\subsection{Convolutional Neural Networks}
+
+     The Convolutional Neural Networks (CNNs) are the current state-of-the-art for the Fashion-MNIST dataset with 96.3\% accuracy \cite{randomerasingdataaugmentationpaper}.For all tests with CNNs the values of the pixels were divided by 255, so that the values are always between 0 and 1.
+The first CNN that we used was based on the 1994s LeNet5 \cite{yannLeCun:1998}, one of the first CNNs, that has a 99.05\% accuracy for the MNIST dataset \cite{yannLeCun:mnist}.
+We used the same layers and kernel sizes but with more features on each convolutional layer.
+\ref{fig:lenet5} shows the architecture used for the first CNN test.
+
+    \begin{figure}[h]
+    \begin{center}
+        \includegraphics[scale=0.8]{lenet5Arch.jpg}
+        \caption{LeNet5 based Architecture\label{fig:lenet5}}
+    \end{center}
+    \end{figure}
+
+    We trained the network for 200 epochs and got an accuracy of 89.02\%, then we added rotations from -5 to 5 degrees and got 89.81\%.
+
+    In orde
+
 \section{Results}
@@
 
-A statement requiring citation \cite{Figueredo:2009dg}.
 \blindtext % Dummy text
@@
 
-\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
-
-\bibitem{LWan:2013dg}
-L. Wan, M. Zeiler, S. Zhang, Y. LeCun, and R. Fergus, “Regularization of neural networks using dropconnect,” Icml, no. 1, pp. 109–111, 2013.
-
-\bibitem{DCirean:2012dg}
-D. Cirean, U. Meier, and J. Schmidhuber, “Multi-column Deep Neural Networks for Image Classification,” International Conference of Pattern Recognition, no. February, pp. 3642–3649, 2012.
-
-\bibitem{ISato:2015dg}
-I. Sato, H. Nishimura, and K. Yokoi, “APAC: Augmented PAttern Classification with Neural Networks,” Arxiv, 2015.
-
-\bibitem{JRChang:2015dg}
-J.-R. Chang and Y.-S. Chen, “Batch-normalized Maxout Network in Network,” Arxiv, 2015.
-
-\bibitem{CYLee:2015dg}
-C.-Y.
-Lee, P.
-W.
-Gallagher, and Z.
-Tu, “Generalizing Pooling Functions in Convolutional Neural Networks: Mixed, Gated, and Tree,” in Proceedings of the 19th International Conference on Artificial Intelligence and Statistics, 2015, pp.
-464–472.
-
-\bibitem{CFran:2017dg}
-Chollet, François. "Many good ideas will not work well on MNIST (e.g. batch norm). Inversely many bad ideas may work on MNIST and no transfer to real CV." 13 April 2017, 11:51 a.m. Tweet.
-
-\bibitem{FashionMNIST}
-Fashion-MNIST: a Novel Image Dataset for Benchmarking Machine Learning Algorithms. Han Xiao, Kashif Rasul, Roland Vollgraf
-
-\bibitem{scikitlearn}
-API design for machine learning software: experiences from the scikit-learn project, Buitinck et al., 2013
-
-\bibitem{scikitlearnbenchmark}
-Zalando Research. Fashion MNIST Scikit-Learn benchmark. http://fashion-mnist.s3-website.eu-central-1.amazonaws.com/
-
-\bibitem{randomerasingdataaugmentationpaper}
-Zhong Z., Zheng L., Kang G., Li S., Yang Y. . Random Erasing Data Augmentation. ArXiv e-prints 1708.04896 2017
-
-\end{thebibliography}
+\bibliography{references}
+\bibliographystyle{plain}
 

### 2017-12-13 vgg.py
vgg random erasing

@@ -20,6 +20,8 @@ from __future__ import print_function
 import numpy as np
 import tensorflow as tf
 import utils.reader
+from numpy import random
+import math
 
 tf.logging.set_verbosity(tf.logging.INFO)
 
@@ -145,6 +147,28 @@ def cnn_model_fn(features, labels, mode):
       mode=mode, loss=loss, eval_metric_ops=eval_metric_ops)
 
 
+def randomErasing(img, probability = 0.5, sl = 0.02, sh = 0.4, r1 = 0.3, mean=0.4914):
+
+  if random.uniform(0, 1) > probability:
+    return img
+
+  for attempt in range(100):
+    area = 28 * 28
+
+    target_area = random.uniform(sl, sh) * area
+    aspect_ratio = random.uniform(r1, 1/r1)
+
+    h = int(round(math.sqrt(target_area * aspect_ratio)))
+    w = int(round(math.sqrt(target_area / aspect_ratio)))
+
+    if w <= 28 and h <= 28:
+      x1 = 0 if 28 - h <= 0 else random.randint(0, 28 - h)
+      y1 = 0 if 28 - w <= 0 else random.randint(0, 28 - w)
+      img[x1:x1+h, y1:y1+w] = mean
+      return img
+
+  return img
+
 def main(unused_argv):
   # Load training and eval data
   # mnist = tf.contrib.learn.datasets.load_dataset("mnist")
@@ -163,9 +187,13 @@ def main(unused_argv):
   eval_data = eval_data.astype(np.float32)
   eval_data = np.multiply(eval_data, 1.0 / 255.0)
 
+  for data in train_data:
+    data = data.reshape((28, 28))
+    data.setflags(write=1)
+    data = randomErasing(data).flatten()
+
   train_labels = np.asarray(train_labels, dtype=np.int32)
   eval_labels = np.asarray(eval_labels, dtype=np.int32)
-
 
   # Create the Estimator
   mnist_classifier = tf.estimator.Estimator(
@@ -186,7 +214,7 @@ def main(unused_argv):
       shuffle=True)
   mnist_classifier.train(
       input_fn=train_input_fn,
-      steps=100000,
+      steps=10000,
       hooks=[logging_hook])
 
   # Evaluate the model and print results

### 2017-12-13 article/article.tex
CNNs

@@
 
-    We trained the network for 200 epochs and got an accuracy of 89.02\%, then we added rotations from -5 to 5 degrees and got 89.81\%.
+    We trained the network for 200 epochs and got an accuracy of 89.02\%, then, to increase the examples in the training set, we added rotations from -5 to 5 degrees and got 89.81\%.
 
-    In orde
+    Seeking to improve our accuracy, we used a more complex and deeper CNN as base, the Very Deep Convolutional Networks \cite{DBLP:journals/corr/SimonyanZ14a} used in the  ImageNet Challenge.
+Since this is a deep CNN and made for 224x224 RGB images, we adapted to a smaller network with a receptive field of 28x28 and fewer units on the fully connected layer.
+\ref{fig:vgg} shows the architecture of the new CNN.
+
+    \begin{figure}[h]
+    \begin{center}
+        \includegraphics[scale=0.65]{vggArch.jpg}
+        \caption{VGG based Architecture\label{fig:vgg}}
+    \end{center}
+    \end{figure}
+
+    The accuracy obtained from training the new network for 300 epochs was 90.06\%, and for 938 epochs, 91.27\%.
 

### 2017-12-13 article/article.tex
text update

--- 2017-12-13 article/article.tex
@@
 
-\section{Methods}
+\section{Approaches}
 
-Maecenas sed ultricies felis. Sed imperdiet dictum arcu a egestas. 
-\begin{itemize}
-\item Donec dolor arcu, rutrum id molestie in, viverra sed diam
-\item Curabitur feugiat
-\item turpis sed auctor facilisis
-\item arcu eros accumsan lorem, at posuere mi diam sit amet tortor
-\item Fusce fermentum, mi sit amet euismod rutrum
-\item sem lorem molestie diam, iaculis aliquet sapien tortor non nisi
-\item Pellentesque bibendum pretium aliquet
-\end{itemize}
-\blindtext % Dummy text
+\subsection{Random Classifier}
 
-Text requiring further explanation\footnote{Example footnote}.
+To test our framework, we implemented a random classifier that simply guesses one of the 10 classes. The accuracy was 10\% as expected.
 
-%------------------------------------------------
+\subsection{K-Nearest-Neighbors (KNN)}
 
-\section{Approaches}
+\subsubsection{Own implementation}
+
+Our first attempt at the problem was implementing the K-Nearest-Neighbors algorithm ourselves.
+We tried using the Euclidean distance as the metric and K = 50 as the parameters for the algorithm.
+For that, we obtained an accuracy of 75.80\%, quite far from the scikit-learn benchmark.
+
+This algorithm was pretty fast to implement.
+Since its training consists in only saving the training set, it is pretty fast.
+However, it does take a lot of time to classify each example.
+
+\subsubsection{Distance from Mean}
+
+Inspired by the KNN algorithm, we implemented a "distance from mean" algorithm in which for the training we
+take the mean of each group of instances of the same class and for the testing we simply classify as the nearest
+of the 10 means obtained in the training part.
+
+This is basically a worse version of the KNN and the results were worse accordingly.
+We obtained an accuracy of 67.68\%.
+The benefits were the fact that it was easy to implement, fast to train and fast to classify.
+
+\subsubsection{Scikit-Learn Implementation}
+
+We also tested for the Scikit-Learn implementation for the KNN algorithm.
+This time, we tested for K = 5 neighbors using the Manhattan distance.
+Our obtained accuracy was 86.23\%, the exact accuracy from the benchmark, as expected.
+
+\subsubsection{Scikit-Learn w/ Haar Transform Pre-Processing}
+
+For the next test, we tried to pre-process the dataset by changing the feature space. We  maintained the parameters K = 5 and
+Manhattan distance, but also used the Haar transform to change the feature space. The idea was to use features that described the frequencies
+in the image, allowing a more global description of the image. However, it did not achieve good results, resulting in an accuracy of 84.0\%, lower than
+the algorithm without the Haar Transform pre-processing.
+
+\subsection{Single Layer Perceptron}
+
+\subsubsection{Standard Implementation}
+
+We implemented ourselves a single layer perceptron and trained it with only 1 iteration over the dataset.
+We did not invest a lot of effort in this approach because it relies on the assumption that the dataset
+is linearly separable for the algorithm to converge, which clearly is not the case for the dataset.
+We obtained an accuracy of 75.8\% for this approach
+
+\subsubsection{MIRA (Margin-infused relaxed algorithm)}
+
+We made some changes to the update step of the algorithm so it took into account how much
+each error should affect the weights of the perceptron, using the Margin-infused relaxed algorithm
+technique. We obtained slightly better result, with an accuracy of 76.99\%.
+
+\subsection{SVM (Scikit-Learn Implementation)}
+
+\subsubsection{Polynomial Kernel}
+
+For the SVM we used the Scikit-Learn implementation. We first tested with a 3rd degree polynomial kernel and with a penalty parameter C = 10, since
+it was the parameters used for the benchmark. We obtained an accuracy of 87.23\%, which is slightly different from the accuracy described in the benchmark (87,23\%).
+
+\subsubsection{Polynomial Kernel w/ Pre-Processing}
+
+We tried to improve the results by pre-processing the dataset by downscaling the images to 7x7, normalizing the dataset by feature (pixel) and also adding
+to the algorithm input rotations of the original dataset from -10 to 10 degrees, varying degree by degree.
+With that technique, we obtained an accuracy of 84.91\%, which was worse than without the pre-processing. We suspect that down sampling the dataset
+to 7x7 images caused too much information loss.
+
+Because of that, we changed the down sampling to 14x14 and also changed the rotation interval to the interval -5 to 5 degrees.
+The new accuracy was 89.39\%, an improvement of about 2\% compared to the example without the pre-processing.
+
+It is also important to note that the pre-processing heavily improved the accuracy of the algorithm when using a small subset of the
+original dataset. For instance, for 100 instances, the accuracy was improved from 43.69\% to 64.21\% and for 1000 instances it was
+improved from 59.10\% to 78.56\%. It is probably due to the fact that adding the rotation benefits a lot small datasets that do not contain
+enough data for the generalization necessary for good results.
+
+\subsubsection{Gaussian Kernel}
+
+We also tested for a gaussian kernel, with parameter C = $10^6$ and gamma = $4 10^-7$ since it achieved good results from previous works.
+As expected, we obtained better accuracy, achieving 90.13\% for those parameters.
+
+\subsubsection{Gaussian Kernel w/ Rotations and Canny Filterl}
+
+By adding rotations from -5 to 5 degrees, without down sampling, and also applying the canny filter (an edge detection filter)
+for the dataset, we achieved a result of 80.36\%. Even though we thought that applying the canny filter was a good idea to improve
+the significance features of the image, it clearly was not the case.
 
@@
 
-     The Convolutional Neural Networks (CNNs) are the current state-of-the-art for the Fashion-MNIST dataset with 96.3\% accuracy \cite{randomerasingdataaugmentationpaper}.For all tests with CNNs the values of the pixels were divided by 255, so that the values are always between 0 and 1.
+     The Convolutional Neural Networks (CNNs) are the current state-of-the-art for the Fashion-MNIST dataset with 96.3\% accuracy \cite{randomerasingdataaugmentationpaper}.
+For all tests with CNNs the values of the pixels were divided by 255, so that the values are always between 0 and 1.
 The first CNN that we used was based on the 1994s LeNet5 \cite{yannLeCun:1998}, one of the first CNNs, that has a 99.05\% accuracy for the MNIST dataset \cite{yannLeCun:mnist}.
@@
 
-\section{Results}
-
-\begin{table}
-\caption{Example table}
-\centering
-\begin{tabular}{llr}
-\toprule
-\multicolumn{2}{c}{Name} \\
-\cmidrule(r){1-2}
-First name & Last Name & Grade \\
-\midrule
-John & Doe & $7.5$ \\
-Richard & Miles & $2$ \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\blindtext % Dummy text
-
-\begin{equation}
-\label{eq:emc}
-e = mc^2
-\end{equation}
-
-\blindtext % Dummy text
-
-%------------------------------------------------
-
-\section{Discussion}
-
-\subsection{Subsection One}
-
-\blindtext % Dummy text
-
-\subsection{Subsection Two}
-
-\blindtext % Dummy text
-
 %----------------------------------------------------------------------------------------

### 2017-12-13 vgg.py

@@ -214,7 +214,7 @@ def main(unused_argv):
       shuffle=True)
   mnist_classifier.train(
       input_fn=train_input_fn,
-      steps=10000,
+      steps=20000,
       hooks=[logging_hook])
 
   # Evaluate the model and print results

### 2017-12-13 article/article.tex
dataset section

--- 2017-12-13 article/article.tex
@@
 
-\documentclass[twoside,twocolumn]{article}
+\documentclass{article}
 
@@
 \renewcommand{\maketitlehookd}{%
-\begin{abstract}
-\noindent \blindtext % Dummy abstract text - replace \blindtext with your abstract text
-\end{abstract}
+
 }
@@
 With that in mind, the Fashion MNIST dataset \cite{FashionMNIST} was created. It has same size and format
-of the MNIST dataset (70.000 grayscale images of size 28x28 labeled into 10 different classes) meaning that
+of the MNIST dataset meaning that
 it should be as simple to use, but its images consist of fashion items which are supposedly harder to
@@
 in the Fashion MNIST dataset. We want to measure the accuracy of our tests and compare them with different
-results on the same dataset, while also trying to obtain some intuition behind the data.
+results on the same dataset, while also trying to obtain some intuition behind the data.\
+
+\section{DataSet}
+
+	The Fashion MNIST dataset is composed by 70.000 grayscale(0-255) images of size 28x28 labeled into the following 10 different classes: T-shirt/top, Trouser, Pullover, Dress, Coat, Sandal, Shirt, Sneaker, Bag and Ankle boot.\ref{fig:fashionex} is an example of one of the images in the dataset.
+
+	\begin{figure}[h]
+    \begin{center}
+        \includegraphics[scale=0.8]{fashionExample.png}
+        \caption{Image Example\label{fig:fashionex}}
+    \end{center}
+    \end{figure}
+
+    For the implementation we used Python and sklearn\cite{scikitlearn} and tensorflow \cite{tensorflow} libraries. The input for the algorithms are the pixels values.
 
@@
 The Fashion MNIST repository contains some benchmarks using the python library
-scikit-learn \cite{scikitlearn} \cite{scikitlearnbenchmark}. They are not meant
+scikit-learn \cite{scikitlearnbenchmark}. They are not meant
 to be efficient or good, but they work as a baseline for our project.
@@
     The accuracy obtained from training the new network for 300 epochs was 90.06\%, and for 938 epochs, 91.27\%.
+When we tried to increase the number of epochs again, the accuracy dropped slightly, so we went to another approach.
+\ref{fig:lossRateVGG} shows the value of the loss rate given the number of steps.
+
+    \begin{figure}[h]
+    \begin{center}
+		\includegraphics[scale=0.6]{lossRateVGG.png}
+        \caption{Loss Rate for VGG based network\label{fig:lossRateVGG}}    
+    \end{center}
+    \end{figure}
+
+    Our next approach was to use Random Erasing as data augmentation, since it was used in the state-of-the-art implementation. Random Erasing randomly
+selects a rectangle region in an image and erases its pixels with random values, which reduces the risk of over-fitting.
+For 300 epochs the accuracy was .
+Seeing that adding only the Random Erasing technique decreased the accuracy, we combined it with the rotation from -5 to 5 degrees.
 

### 2017-12-13 article/article.tex
merge
conclusion

@@
 
-\documentclass{article}
+\documentclass[twoside,twocolumn]{article}
 
@@
 For all tests with CNNs the values of the pixels were divided by 255, so that the values are always between 0 and 1.
+To be able to train faster and with larger networks, we used the GPU NVIDIA GDX980N that uses CUDA.
+
       The first CNN that we used was based on the 1994s LeNet5 \cite{yannLeCun:1998}, one of the first CNNs, that has a 99.05\% accuracy for the MNIST dataset \cite{yannLeCun:mnist}.
@@
     Our next approach was to use Random Erasing as data augmentation, since it was used in the state-of-the-art implementation. Random Erasing randomly
-selects a rectangle region in an image and erases its pixels with random values, which reduces the risk of over-fitting.
-For 300 epochs the accuracy was .
-Seeing that adding only the Random Erasing technique decreased the accuracy, we combined it with the rotation from -5 to 5 degrees.
+selects a rectangle region in an image and erases its pixels with random values, which reduces the risk of over-fitting. For 300 epochs the accuracy was .
+
+	\section{Conclusions}
+
+	After running all the different algorithms we could realize the importance of a powerfull resource for processing, in our case the GPU; of a usefull pre-processing, otherwise we could decrease the amount of information in the data and worsen the result; the efficiency of the Convolutional Neural Networks for a task of this kind, because they got the higher results sometimes even in less time.
+
+	Our results were above the ones in the benchmark, but still lower than the state-of-the-art.
+The state-of-the-art used a more complex network, with more pre-processing, this is what we believe was the cause for the difference between our accuracy and the state-of-the-art.
+
+	Our next steps to improve the accuracy of the result are to add more data augmentation combined with the Random Erasing (i.e flipping, rotation and cropping) and implement and test different networks with tensorflow, such as the ResNet, which is similar to the CNN used in the state-of-the-art implementantion.
+We are also extending the currents implementations to more complex data sets like CIFAR-10 and CIFAR-100, that are datasets with 32x32 RGB images with respectively 10 and 100 different labeled classes.
 

### 2017-12-13 article/article.tex
tex

--- 2017-12-13 article/article.tex
@@
 
-\section{DataSet}
+\section{The Dataset}
 
-	The Fashion MNIST dataset is composed by 70.000 grayscale(0-255) images of size 28x28 labeled into the following 10 different classes: T-shirt/top, Trouser, Pullover, Dress, Coat, Sandal, Shirt, Sneaker, Bag and Ankle boot.\ref{fig:fashionex} is an example of one of the images in the dataset.
+    The Fashion MNIST dataset is composed by 70.000 grayscale (0-255) images of size 28x28 labeled into the following 10 different classes: T-shirt/top, Trouser, Pullover, Dress, Coat, Sandal, Shirt, Sneaker, Bag and Ankle boot.
+Figure \ref{fig:fashionex} is an example of one of the images in the dataset.
+
+    For the implementation we used Python and Scikit-Learn \cite{scikitlearn} and TensorFlow \cite{tensorflow} libraries. The input for the algorithms are the pixels values.
 
@@
         \includegraphics[scale=0.8]{fashionExample.png}
-        \caption{Image Example\label{fig:fashionex}}
+        \caption{Example of an image in the dataset\label{fig:fashionex}}
     \end{center}
     \end{figure}
-
-    For the implementation we used Python and sklearn\cite{scikitlearn} and tensorflow \cite{tensorflow} libraries. The input for the algorithms are the pixels values.
 
@@
 The current state of art for the Fashion MNIST dataset is a recent one, with 96.3\% accuracy using Wide
-Residual Networks using random erasing data augmentation \cite{randomerasingdataaugmentationpaper}.
+Residual Networks using random erasing data augmentation \cite{randomerasingdataaugmentationpaper} and other image pre-processing techniques.
 We will consider this as the ceiling accuracy for our project.
@@
 This algorithm was pretty fast to implement.
-Since its training consists in only saving the training set, it is pretty fast.
+Since its training consists in only saving the training set, it is pretty fast to train.
 However, it does take a lot of time to classify each example.
@@
 For the SVM we used the Scikit-Learn implementation. We first tested with a 3rd degree polynomial kernel and with a penalty parameter C = 10, since
-it was the parameters used for the benchmark. We obtained an accuracy of 87.23\%, which is slightly different from the accuracy described in the benchmark (87,23\%).
+they were the parameters used for the benchmark. We obtained an accuracy of 87.23\%, which is slightly different from the accuracy described in the benchmark (89,7\%).
 
@@
 
-We also tested for a gaussian kernel, with parameter C = $10^6$ and gamma = $4 10^-7$ since it achieved good results from previous works.
+We also tested for a gaussian kernel, with parameter C = $10^6$ and gamma = $4  \cdot 10^{-7}$ since it achieved good results from previous works.
 As expected, we obtained better accuracy, achieving 90.13\% for those parameters.
@@
 
-     The Convolutional Neural Networks (CNNs) are the current state-of-the-art for the Fashion-MNIST dataset with 96.3\% accuracy \cite{randomerasingdataaugmentationpaper}.
-For all tests with CNNs the values of the pixels were divided by 255, so that the values are always between 0 and 1.
+     The Convolutional Neural Networks (CNNs) are the current state of the art for the Fashion-MNIST dataset with 96.3\% accuracy \cite{randomerasingdataaugmentationpaper}.
+To be able to train faster and with larger networks, we used the GPU NVIDIA GTX 980M with CUDA.
+
       The first CNN that we used was based on the 1994s LeNet5 \cite{yannLeCun:1998}, one of the first CNNs, that has a 99.05\% accuracy for the MNIST dataset \cite{yannLeCun:mnist}.
@@
 
-    We trained the network for 200 epochs and got an accuracy of 89.02\%, then, to increase the examples in the training set, we added rotations from -5 to 5 degrees and got 89.81\%.
+    We trained the network for 200 epochs and got an accuracy of 89.02\%, then, to increase the examples in the training set, we added rotations from -5 to 5 degrees, degree by degree, and got 89.81\%.
 
@@
     Our next approach was to use Random Erasing as data augmentation, since it was used in the state-of-the-art implementation. Random Erasing randomly
-selects a rectangle region in an image and erases its pixels with random values, which reduces the risk of over-fitting.
-For 300 epochs the accuracy was .
-Seeing that adding only the Random Erasing technique decreased the accuracy, we combined it with the rotation from -5 to 5 degrees.
+selects a rectangle region in an image and erases its pixels with random values, which reduces the risk of over-fitting. For 300 epochs the accuracy was .
+
+	\section{Conclusions}
+
+	After running all the different algorithms we could realize the importance of a powerfull resource for processing, in our case the GPU.
+We also have seen the importance of choosing good pre-processing techniques, that can either boost or decrease the quality of the test.
+	Also, we have witnessed the efficiency of the Convolutional Neural Networks for a task of this kind, because they got the higher results sometimes even in less time.
+
+	Our results were above the ones in the benchmark, but still lower than the state of art.
+The state of art used a more complex network, with more pre-processing, which is what we believe that was the cause for the difference between our accuracy.
+
+	Our next steps to improve the accuracy of the result are to add more data augmentation combined with the Random Erasing (i.e flipping, rotation and cropping) and to implement and test different networks with TensorFlow, such as the ResNet, which is similar to the CNN used in the state of the art implementation.
+	We are also extending the currents implementations to more complex data sets like CIFAR-10 and CIFAR-100, that are datasets with 32x32 RGB images with respectively 10 and 100 different labeled classes.
 
